---
title: "Lab 5"
author: "Andrea Cornelius"
date: "10/26/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    number_sections: yes
    code_folding: hide
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Confidence intervals

In this section, we'll learn to use the 't.test()' function as a way to return the confidence interval using the t-distribution.

## Example 1

Create a mock sample of observation values and find the confidence interval. Then we'll learn how to report that.

```{r}
pika_mass <- c(82, 94, 110, 70, 86, 99, 102, 320)

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)

pika_ci
```
### Risky and tedious way

Mean pika mass at Paiute Pass is 91.9 g $\pm$ 13.5 g (mean $\ 1 standard deviation, n = 7) with a 95% confidence interval of [79.4, 104.4] g.

### A high initial investment, but safer and better way

In-line code referencing to stored objects!

Use a single backtick on either side of a lowercase r to create an in-line bit of code.
Use control/return over ticks to view value, hovering over.

Mean pika mass at Paiute Pass is `r round(pika_mean, 1)` g $\pm$ `r round(pika_sd, 1)` g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r pika_ci$conf.int[1]`], `r pika_ci$conf.int[2]`] g.

